### 2023-08-22 manuscript.tex
Pretty `mailto` link [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/c050bb80f13115ddab1a67428d31c5177ce08ee7.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/c050bb80f13115ddab1a67428d31c5177ce08ee7/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5937561720

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...d49ab3e8164a4169e27e9555874ff7f107c09650\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/d49ab3e8164a4169e27e9555874ff7f107c09650/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/d49ab3e8164a4169e27e9555874ff7f107c09650}{habi/EAWAG-manuscript@d49ab3e}
on August 21, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
✉ --- Correspondence possible via email or \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues} (preferrably).
or email to
David Haberthür \textless david.haberthuer@unibe.ch\textgreater.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Available: \url{https://osf.io/ecmz4}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 21 Aug 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 21 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 21 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{archived here}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{A revised version \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.1}{\texttt{v1.1}} (\href{https://habi.github.io/EAWAG-manuscript/v/c49d0b8ac8f078c226318972b06e8c4a39100bb2/}{archived here}) has been submitted.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/df99415...c050bb80f13115ddab1a67428d31c5177ce08ee7\#files_bucket}{is further updated} since re-submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/c050bb80f13115ddab1a67428d31c5177ce08ee7/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/c050bb80f13115ddab1a67428d31c5177ce08ee7}{habi/EAWAG-manuscript@c050bb8}
on August 22, 2023.

@@

\leavevmode\vadjust pre{\hypertarget{correspondence}{}}%
✉ --- Correspondence via \href{https://github.com/habi/EAWAG-manuscript/issues}{GitHub Issues}
or email to
\href{mailto:david.haberthuer@unibe.ch?subject=Feedback\%20for\%20\%22Microtomographic\%20investigation\%20of\%20a\%20large\%20corpus\%20of\%20cichlids\%22\&body=Write\%20your\%20feedback\%20here.}{David Haberthür}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-3rxGCEvJ}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Summers AP. CT Scans - \#ScanAllFish. 2015 {[}cited 22 Aug 2023{]}. Available: \url{https://osf.io/ecmz4/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{OpenSCAD. {[}cited 22 Aug 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.08.1+1.g86b56a7.dirty documentation. {[}cited 22 Aug 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 22 Aug 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
